### 2016-11-07 paper1.tex
Fixed some formatting ugliness in Paper 1

{\bf We implemented this method in the SPH code {\sc GASOLINE}
\citep{Wadsley2004} with updates described in \cite{Shen2010}.  These
include a sub-grid model for turbulent mixing of metals and energy.  The
heating and cooling include photoelectric heating of dust grains, UV heating
and ionization and cooling due to hydrogen, helium and metals.

@@

These modifications, along with detailed testing, will be discussed in a
forthcoming paper on {\sc GASOLINE2}.  For reference, the quality of our results
on the tests discussed here is similar to the results presented for other modern
modified SPH codes \citep[e.g.][]{Hopkins2013}.   }

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_hottemp.eps}
    \caption[Peak temperature of feedback-heated gas in a superbubble]{Peak
    temperature of feedback-heated gas inside the isolated star cluster's hot
    bubble.  Evaporation quickly enters the self-regulating regime, and the
    temperature is roughly constant for the last $15\;\mathrm{Myr}$ of
    feedback.}
    \label{onestar_hottemp}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_kappa.eps}
    \caption[Dependence of superbubble heated gas on conduction coefficient]{Hot
    mass production as a function of the conduction coefficient $\kappa_0$.  As
    this figure shows, reducing $\kappa_0$ by a factor of 100 reduces the amount
    of hot mass generated through conduction by only a factor of $\sim2$. All
    $\kappa_0$ values have units of $\mathrm{erg\; s^{-1} K^{-7/2} cm^{-1}}$.}
    \label{onestar_kappa}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_clumpypoints.eps}
    \caption[Image of superbubbles in a clumpy ISM]{3 kpc wide slices
    from the same three methods shown in figure~\ref{onestar_column}, also at 50
    Myr, but applied to a star cluster in an inhomogeneous medium.  Particles
    whose smoothing length intersects z=0~kpc are shown.  Particles above $10^5$
    K are shown in red.  The upper row shows simulations with a single clump,
    while the bottom row shows simulations with 6 clumps.}
    \label{onestar_clumpyslice}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/disc_phase.eps}
    \caption[Phase diagram of gas in isolated galaxies]{Phase diagrams for the
    Milky Way (left) and dwarf (right) simulations at $200\;\mathrm{Myr}$.  The
    central panel shows a typical path for gas ejected from the Milky Way.
    First gas cools radiatively (cyan path) to high density, where it becomes
    multiphase as its hot component is heated to $\sim10^7\;\mathrm{K}$ by
    feedback (red path) from nearby stars formed from its neighbouring high
    density gas.  The hot phase cools primarily through adiabatic expansion
    (green path).  This process is often repeated one or more times, with gas
    that is entirely hot phase being ejected from the disc.  Cooling times of
    $10^4\;\mathrm{yr}$ and $10^6\;\mathrm{yr}$ are shown in blue. {\bf The
    majority of the hot gas in the upper left quadrant of the phase diagram has
    cooling times $>10^8\;\mathrm{yr}$.  The cooling curve for
    $10^8\;\mathrm{yr}$ passes through the green curve.}  Note that particles in
    the multiphase state show the temperature and density for each state as
    separate points.  The mean properties of multiphase particles would place
    them in regions with short cooling times.}
    \label{disc_phase}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/kennicutt_schmidt.eps}
    \caption[Kennicutt-Schmidt law for isolated galaxies]{Kennicutt-Schmidt law
    in the Milky Way-like (blue points) and dwarf (red triangles) galaxies at
    $500\;\mathrm{Myr}$. Surface densities were calculated in radial annuli.
    The dashed line shows the Kennicutt-Schmidt Law.  The superbubble model is
    easily able to regulate star formation rates to within this range.}
    \label{kennicutt_schmidt}
\end{figure}

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/multiphase_properties.eps}
    \caption[Properties of multiphase particles]{Properties of multiphase
    particles in the galaxy simulations.  The top figure shows duration of
    multiphase state for particles in both galaxy simulations.  Particles that
    are in the multiphase state more than once (convert back to single phase,
    cool, and then receive feedback again) have each time they are multiphase
    counted separately. The bottom figure shows maximum heights reached by
    particles in the multiphase state.  For each particle that is ever in the
    multiphase state, the maximum height it reaches {\it while still multiphase}
    is shown above for both galaxy simulations.  Dashed lines show scale heights
    at $10^4\;\mathrm{K}$ for each of the two simulations.}
    \label{multiphase_properties}
\end{figure}

>>>>

We implemented this method in the SPH code {\sc GASOLINE}
\citep{Wadsley2004} with updates described in \cite{Shen2010}.  These
include a sub-grid model for turbulent mixing of metals and energy.  The
heating and cooling include photoelectric heating of dust grains, UV heating
and ionization and cooling due to hydrogen, helium and metals.

@@

These modifications, along with detailed testing, will be discussed in a
forthcoming paper on {\sc GASOLINE2}.  For reference, the quality of our results
on the tests discussed here is similar to the results presented for other modern
modified SPH codes \citep[e.g.][]{Hopkins2013}.

\begin{figure}
    \includegraphics[width=\textwidth]{figures1/onestar_hottemp.eps}
    \caption[Peak temperature of feedback-heated gas in a superbubble]{Peak
    temperature of feedback-heated gas inside the isolated star cluster's hot
    bubble.  Evaporation quickly enters the self-regulating regime, and the
    temperature is roughly constant for the last $15\;\mathrm{Myr}$ of
    feedback.}
    \label{onestar_hottemp}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures1/onestar_kappa.eps}
    \caption[Dependence of superbubble heated gas on conduction coefficient]{Hot
    mass production as a function of the conduction coefficient $\kappa_0$.  As
    this figure shows, reducing $\kappa_0$ by a factor of 100 reduces the amount
    of hot mass generated through conduction by only a factor of $\sim2$. All
    $\kappa_0$ values have units of $\mathrm{erg\; s^{-1} K^{-7/2} cm^{-1}}$.}
    \label{onestar_kappa}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures1/onestar_clumpypoints.eps}
    \caption[Image of superbubbles in a clumpy ISM]{3 kpc wide slices
    from the same three methods shown in figure~\ref{onestar_column}, also at 50
    Myr, but applied to a star cluster in an inhomogeneous medium.  Particles
    whose smoothing length intersects z=0~kpc are shown.  Particles above $10^5$
    K are shown in red.  The upper row shows simulations with a single clump,
    while the bottom row shows simulations with 6 clumps.}
    \label{onestar_clumpyslice}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/disc_phase.eps}
    \caption[Phase diagram of gas in isolated galaxies]{Phase diagrams for the
    Milky Way (left) and dwarf (right) simulations at $200\;\mathrm{Myr}$.  The
    central panel shows a typical path for gas ejected from the Milky Way.
    First gas cools radiatively (cyan path) to high density, where it becomes
    multiphase as its hot component is heated to $\sim10^7\;\mathrm{K}$ by
    feedback (red path) from nearby stars formed from its neighbouring high
    density gas.  The hot phase cools primarily through adiabatic expansion
    (green path).  This process is often repeated one or more times, with gas
    that is entirely hot phase being ejected from the disc.  Cooling times of
    $10^4\;\mathrm{yr}$ and $10^6\;\mathrm{yr}$ are shown in blue. The
    majority of the hot gas in the upper left quadrant of the phase diagram has
    cooling times $>10^8\;\mathrm{yr}$.  The cooling curve for
    $10^8\;\mathrm{yr}$ passes through the green curve.  Note that particles in
    the multiphase state show the temperature and density for each state as
    separate points.  The mean properties of multiphase particles would place
    them in regions with short cooling times.}
    \label{disc_phase}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures1/kennicutt_schmidt.eps}
    \caption[Kennicutt-Schmidt law for isolated galaxies]{Kennicutt-Schmidt law
    in the Milky Way-like (blue points) and dwarf (red triangles) galaxies at
    $500\;\mathrm{Myr}$. Surface densities were calculated in radial annuli.
    The dashed line shows the Kennicutt-Schmidt Law.  The superbubble model is
    easily able to regulate star formation rates to within this range.}
    \label{kennicutt_schmidt}
\end{figure}

\begin{figure}
    \includegraphics[width=\textwidth]{figures1/multiphase_properties.eps}
    \caption[Properties of multiphase particles]{Properties of multiphase
    particles in the galaxy simulations.  The top figure shows duration of
    multiphase state for particles in both galaxy simulations.  Particles that
    are in the multiphase state more than once (convert back to single phase,
    cool, and then receive feedback again) have each time they are multiphase
    counted separately. The bottom figure shows maximum heights reached by
    particles in the multiphase state.  For each particle that is ever in the
    multiphase state, the maximum height it reaches {\it while still multiphase}
    is shown above for both galaxy simulations.  Dashed lines show scale heights
    at $10^4\;\mathrm{K}$ for each of the two simulations.}
    \label{multiphase_properties}
\end{figure}
